\LARGE \bf WORKING TITLE: Incorporating User Feedback in Motion Planning for Manipulators

### 2014-09-29 paper2015asml.tex
adding text to feature section

@@

\begin{figure}
    \includegraphics[trim = 0mm 0mm 0mm 0mm, width=\columnwidth]{pictures/amazon_survey_screenshot}
    \caption{The main survey question which prompts the participant for a rating in four motion characteristics (efficiency, elegance, smoothness and overall impression) after presenting a video that demonstrates the motion from four clearly visible vantage points for any sample trajectory.}
    \label{fig:survey_question}
\end{figure}

@@

\begin{figure}
\includegraphics[trim = 0mm 0mm 0mm 0mm, width=\columnwidth]{pictures/amazon_control_question}
\caption{The survey control question which prompts the participant about the action of the robot in the accompanying video. The question we adopted was to ask the particpant which colored cube the robot touched.}
\label{fig:control_question}
\end{figure}

In addition to the rating and demographic questions, a control question was incorporated to account for satisficing in online surveys~\cite{krosnick1991response}~\cite{krosnick1996satisficing}. The question format can be seen in Figure~\ref{fig:control_question}. This question served as the first counter-measure against satisficing in the survey. The other counter-measure was to manually inspect the responses, and assess whether it agrees with the other survey respondents on a participant-by-participant and then trajectory-by-trajectory basis. The process for examining a particular participant involves seeing how his/her ratings agree or disagree with the average ratings of all the other ratings for this particular trajectory. Aggregating this over all the trajectories the participant rated gives us an idea of how much we can trust their responses and make a decision about rejecting all or none of their responses. Another heuristic we employed in inspecting the responses was looking for the average time to complete the survey to be extremely low, which could hint at strong satisficing.

\section{Survey Results}
\label{sec:analysis}
The results of the survey are summarized in Fig.~\ref{fig:survey_raw} which shows a histogram of (average) responses for each of the four survey questions across the 100 trajectories that were rated by users. It is clear that a majority of the trajectories in our survey were well received by the human observers but there were quite a few trajectories that were rated badly as well. 
\begin{figure}[t]
  \centering{\includegraphics[width=\linewidth]{pictures/efficiency.pdf}}
  \centering{\includegraphics[width=\linewidth]{pictures/elegant.pdf}}
  \centering{\includegraphics[width=\linewidth]{pictures/smooth.pdf}}
  \centering{\includegraphics[width=\linewidth]{pictures/overall.pdf}}
  \caption{Histogram of averaged ratings for the 103 different trajectories. Clockwise from top left: Efficient vs. Inefficient, Elegant vs. Inelegant, Smooth vs. Rough, Overall Rating}
\label{fig:survey_raw}
\end{figure}

@@

\subsection{Feature Design for Trajectory Classification}

>>>>

\todo cite OMPL and optimal planning

\todo formulae for optimization objectives?

@@

\begin{figure}
    \frame{\includegraphics[trim = 0mm 0mm 0mm 0mm, width=\columnwidth]{pictures/amazon_survey_screenshot}}
    \caption{The main survey question which prompts the participant for a rating in four motion characteristics (efficiency, elegance, smoothness and overall impression) after presenting a video that demonstrates the motion from four clearly visible vantage points for any sample trajectory.}
    \label{fig:survey_question}
\end{figure}

@@

\begin{figure}
\frame{\includegraphics[trim = 0mm 0mm 0mm 0mm, width=\columnwidth]{pictures/amazon_control_question}}
\caption{The survey control question which prompts the participant about the action of the robot in the accompanying video. The question we adopted was to ask the particpant which colored cube the robot touched.}
\label{fig:control_question}
\end{figure}

In addition to the rating and demographic questions, a control question was incorporated to account for satisficing in online surveys~\cite{krosnick1991response}~\cite{krosnick1996satisficing}. The question format can be seen in Figure~\ref{fig:control_question}. This question served as the first counter-measure against satisficing in the survey.

The other counter-measure was to manually inspect the responses, and assess whether it agrees with the other survey respondents on a participant-by-participant and then trajectory-by-trajectory basis. The process for examining a particular participant involves seeing how his/her ratings {\em agree or disagree} with the average ratings of all the other ratings for this particular trajectory. Aggregating this over all the trajectories the participant rated gives us an idea of how much we can trust their responses and make a decision about rejecting {\em all or none} of their responses.

Another heuristic we employed in inspecting the responses was looking for the average time to complete the survey to be extremely low, which could hint at strong satisficing.

We found that for our set of data, all the participant ratings for a given trajectory for the were usually within one standard deviation of the average rating for that trajectory. This leads us towards rejecting none of the data we received after running the survey.

\section{Survey Results}
\label{sec:analysis}
The results of the survey are summarized in Fig.~\ref{fig:survey_raw} which shows a histogram of (average) responses for each of the four survey questions across the 100 trajectories that were rated by users. It is clear that a majority of the trajectories in our survey were well received by the human observers but there were quite a few trajectories that were rated badly as well. 
\begin{figure}[t]
  \centering{\includegraphics[width=0.45\linewidth]{pictures/efficiency}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/elegant}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/smooth}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/overall}}
  \caption{Histogram of averaged ratings for the 103 different trajectories. Clockwise from top left: Efficient vs. Inefficient, Elegant vs. Inelegant, Smooth vs. Rough, Overall Rating}
\label{fig:survey_raw}
\end{figure}

@@

\section{Feature Design for Trajectory Classification}

The trajectory features we selected for the classification task consider the environment, the shape of the trajectory and the dynamics-related quantities. These make up our unary features computed only on the input trajectory.

We also include features that compare each trajectory to a nominal trajectory for its problem which also serve to characterize how much the trajectory deviates from the "expected" path. We go over the selection of the nominal path in Section~\ref{subsec:multi_traj_feat}.

\subsection{Unary Trajectory Features}

\subsubsection{Path length}

\subsubsection{Clearance}

\subsubsection{Smoothness}

\subsubsection{Maximum Acceleration}

\subsubsection{Curvature}

\subsection{Multi-Trajectory Features}
\label{subsec:multi_traj_feat}

Additionally we compared the trajectories to nominal end-effector trajectories that were created using a breadth first search in a 3D voxelized approximation of the planning problem. The solution path is in the workspace of the robot from the start position of the end effector to the end position. The edges used in this search are the 26-connected grid of adjacent neighboring voxels.

The order for the neighboring voxels being generated is decided by the length of the line connecting the voxel centers. This results in the voxel-neighbors that share \emph{faces} being pushed onto the queue before the voxel-neighbors that share an \emph{edges}, which are in turn added before those voxel-neighbors that share a \emph{corner} with the generating state. The authors make special mention of this because it can lead to differently shaped (but the same overall length) paths.

We compared the planned workspace trajectories of the end-effectors of the robot to this canonical trajectory for each planning problem by computing:

\subsubsection{Hausdorff Distance}

\subsubsection{Dynamic Time Warping}
